Model Search in Relational Domains

### 2016-10-20 experiments.tex
experiment discussion

\paragraph {\textbf{Decision Heuristics}} Figure~\ref{prop-dec}(b) presents a 
visualization of different decision heuristics in ACDCL.  We observe that 
the ordered heuristic outperforms other heuristics due to its ability to 
prioritize decisions on meet irreducibles that appear in conditional 
branches.  For straight-line code and most of the bit-vector regression 
suite, random heuristics performs the best.

\Omit{
Whereas activity-based heuristics such as Berkmin heuristic which 
works well in propositional cases performs best for benchmarks 
that encountered the maximum number of conflicts to prove safety, 
thus allowing the heuristics to choose the decison variable among the set of learnt clauses.   
}

>>>>

\paragraph {\textbf{Decision Heuristics}} Figure~\ref{prop-dec}(b) presents a 
visualization of different decision heuristics in ACDCL.  Random heuristic
performs the best for most safe benchmarks and all bit-vector category 
benchmarks.  Whereas, the ordered heuristic performs better for programs 
with conditional branches since it prioritizes decisions on meet 
irreducibles that appear in conditional branches over meet irreducibles 
that involve numerical variables.  Whereas, the runtimes for berkmin 
heuristic is slightly greater than the random and ordered heuristic 
for our benchmarks. 
\Omit{
Whereas activity-based heuristics such as Berkmin heuristic which 
works well in propositional cases performs best for benchmarks 
that encountered the maximum number of conflicts to prove safety, 
thus allowing the heuristics to choose the decison variable among the set of learnt clauses.   
}
